### 2014-06-06 method.tex
done with region selection

As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
Unlike the Cascade-CNN, this process of region selection does not reject regions flat out, but merely reorders them to be processed later.

We consider two ways of selecting regions by their score.
The first is to simply sort the regions by score, and to take batches in that sorted order
We quickly discovered that this naive method does not result in good performance, and in fact can be worse than taking regions in an entirely random order.
We hypothesized that this is because the highest scoring regions may all

\subsubsection{Dynamic feature update}

>>>>

As shown in \autoref{fig:combined}, the quick-to-compute features are used to select batches of regions in a way that orders the regions most likely to contain ground truth objects earlier than other regions.
This process of region selection does not reject regions flat out, but reorders them to be processed later.

We first tried to simply sort the regions by score and take batches in that sorted order.
Surprisingly, this naive method results in poor performance, and in fact can be worse than taking regions in an entirely random order.
We hypothesize that this is because the highest scoring regions may all be overlapping with each other, and only result in one detection after non-maximal suppression and other post-processing of detections.

Guided by this intuition, we consider a more cascade-like and dynamic approach to region selection.
We put regions in a random order, set a threshold such that only half of the unexamined regions score above it, take a batch of the above-threshold regions in their order, update the threshold, and repeat.
